---
title: "week_06_notes"
author: "Andrew Nalundasan"
date: "7/31/2021"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
# load libraries
library(tidyverse)
library(ggiraph)
library(vtable)
library(modelsummary)
library(MultNonParam)
library(agricolae)
```


# Overview video

+ GLM for logit

    - Explicitly say what the 1 value is
    
```{r}


data(mtcars)

vtable(mtcars)

mtcars <- mtcars %>% 
  mutate(Transmission = case_when(
    am == 0 ~ "Automatic", 
    am == 1 ~ "Manual"))
  

mtcars <- mtcars %>% 
  mutate(Trans_for_GLM = Transmission == 'Automatic')

glm(Trans_for_GLM ~ mpg + hp, data = mtcars)

```

+ don't show regression tables to a non-technical audience


```{r}

m <- glm(Trans_for_GLM ~ mpg + hp, data = mtcars)
summary(m)
msummary(m, stars = TRUE)

```


+ word clouds are not very useful but executives love them

    - What are you supposed to be surprised by from word clouds?
    - They won't teach you anything
    
+ plotly but use ggiraph instead

    - This can be written in ggplot syntax
    
```{r}
# this is the way that NHK makes interactive graphs
mtcars <- mtcars %>% 
  mutate(CarName = rownames(mtcars)) %>% 
  mutate(toolt = paste0(CarName, '\nTransmission: ', Transmission))


p <- ggplot(mtcars, aes(x = mpg, y = hp, color = Transmission)) +
  geom_point_interactive(aes(tooltip = toolt)) + 
  theme_classic()

ggiraph(ggobj = p)
```

+ this works great in HTML R markdown

+ Line graphs can be tricky with interactive graphs


# Communication best practices

+ Critical for understanding and creating critical visualizations

+ Know your audience

+ Know how to use tools to communicate
    
    - Visuals: graphs and tables
    - Written: clear and concise
    - Presentatoin: engaging and informative

## Communication basics

+ Know who the comms will be for

1. Know your audience (managers, C-suite, analysts, scientists)
2. What do they need to know?
    
    - Don't show everything you've done
    - Do need to know about the data
    - Do need to know the most important variable and how it makes predictions

3. Type of communication

    - Presentation - can answer questions
    - Written - include necessary info
    - Narrow (team) or broad (company/industry distribution)
    
4. Use visuals

    - Picture superiority effect
    - Improve audience understanding
    - People understand pictures easier than understanding words
    - easier to **detect patterns** with graphs than with tables
    - visualization supports **exploration** and **explanation** of the data
    - think about what the audience can understand
    
+ Don't take summary statistics at face value. 

    - ALWAYS plot out the data to see what it looks like!
    - descriptive statistics may be the same, but visually look different
    - DATASAURUS!!!
    
+ Gestalt principles
    
    1. Similarity
    2. Proximity
    3. Enclosure
    4. Continuation
    5. Figure/Ground (White Space)
    6. Symmetry
    
+ Visualization is for exploration and explanation of the data

    - Exploration:
        - Learning what the data contains
        - Determine which one is the one that communicates what I'm trying to explain the BEST
    - Explanation:
        - Turn exploration into communication
        - Make audience understand things without making them work for it

# Interpreting statistical tests

+ Ho: some activity does NOT impact the variable of interest

+ Ha: some activity DOES impact the variable of interest

+ Determine alpha (risk level) 

    - Sample being used may not truly represent the population
    - Consider the possibility that I get a result that isn't accurate to the population
    - Results could be wrong: 
    - Type I: reject a true null
        - activity or variable does not impact the variable of interest, but the sample indicates that it does
    - Type II: fail to reject a false null
        - in the population, there really is an impact of one variable onto the other, but the sample leads you to continue to believe that it's true
    - **How does the sample represent the population**
    
+ Communicate results to non-technical audience

    - Likely more interested in Practical significance rather than Statistical significance
    - Want to know **HOW MUCH**
    - Communicate Practical significance:
        - State how large the **impact** is
    - Communicate Statistical significance: 
        - State how **reliable** the results are
        - if p-value < alpha:
            - results are reliable (relative to the Ho)
        - else:
            - results unreliable
    - "well, suppose if..."

+ Communicate results to technical audience

    - Make certain that I understand it!!
    - Don't attempt to fake it. You will GET GOT!
    
## Interpret p-values

+ Example: "The mean price of Citrus Hill OJ when there is a special is \$0.03 higher than if there is not a special. If there is no difference between price with and without specials in the underlying population (the Ho), the chance of observing a difference of \$0.03 (or larger) is close to the p-value.

    - Key components:
        - "\$0.03 higher", <- practical significance
        - "there is a special vs not a special" <- condition
        - "if there is no difference" <- Ho 
        - "chance of observing" <- p-value
        - "a difference of \$0.03 is close to" <- the p-value is the probability of observing this difference
  

# Tests of the median

+ can't use t-test or chi-squared test to test medians

    - t-test: specifically for means
    - chi-squared: specifically for proportions
    - medians are difference because they relate to the rank of the observations
        - median marks half-below and half-above
    - CLT: distribution becomes normalized with more observations
    
## Wilcoxon signed-rank test

+ tests whether the mean ranks differ

    - nonparametric: not assuming the distribution of the parameters
    
```{r}
oj <- read_csv('../02_raw_data/OJ_Data.csv')

vtable(oj)

# difference in price when there is no special, difference in price when there is a special
wilcox.test(oj$PriceCH[oj$SpecialCH == 0], oj$PriceCH[oj$SpecialCH == 1], conf.int = TRUE)
```

**Comments**

+ Ha: true location shift is not equal to 0

    - difference in location = 2.838e-05
    - this is a very small difference in the median
        - this does not make much of an impact

+ this is statistically significant, but practical significance is of no impact

## More median tests

+ test whether two samples come from the same distribution

    - Ho is equality of distributions, and not just equality of median
    
```{r}
mood.median.test(oj$PriceCH[oj$SpecialCH == 0], oj$PriceCH[oj$SpecialCH == 1])
```

**Comments**

+ p-value is tiny, so reject the null

```{r}
Median.test(oj$PriceCH, as.factor(oj$SpecialCH), alpha=0.05)
```

**Comments**

+ tiny price difference. Specials don't drive much of a difference

## Use t-test across multiple groups

+ the more questions you ask, the higher probability you have of finding something in the sample that does not exist in the population

+ pairwise test - only two conditions at a time

    - only examining 2 groups at a time

```{r}
# compare 4 groups pairwise using bonferroni adjustment
pairwise.t.test(oj$PriceCH, oj$STORE, p.adjust.method = "bon")
```

**Comments**

+ adjusted the value to compensate for the fact that we've compared 10 different paired t-tests from this dataset

+ store 0 and store 2, and store 3 and store 4 are NOT statistically different

    - store 0 and store 2 == 1.000 <- these are the same
    - store 3 and store 4 == <2e-16 <- these are the same
    

# Think like a designer

+ Must consider my audience

    - What do they know about the data?
    - What do they know about the business?
    - Speak **THEIR** language!

+ What do I want the audience to know/learn?

    - Do they need to make a decision?
    - This will drive how to convey my message
    
+ Design a visual that makes it easy for them to see what they need to know

    - Don't just show the data or say what it is
    - **USE THE DATA AND VISUAL TO ANSWER THE QUESTION!**
    
+ Must think like the audience. Stop thinking like an analyst

+ 3 general design principles

1. Affordances

    - Make it obvious how the visual is meant to be read
    - Ryan Drobny nerdy engineering examples
        - Push/Pull doors, etc.
    1. Highlight the important stuff
        - Make my point obvious
    2. Eliminate Distraction
    3. Create a visual hierarchy
    
  
2. Accessibility

    - Know your audience so the visual is accessible to them
    1. Don't over coplicate. Keep it simple, stupid.
        - Must be able to convey the point I'm trying to make
    2. Use text to explain
    

3. Aesthetics

    - People are more likely to read something that is pleasing to the eye
    1. Take the time to make it pretty, elegant, a pleasure to read
    2. Use color intentionally - don't just use the default colors
    3. Align vertical and horizontal spaces
    4. OK to have white space
    

# Specialty packages

## PA#7

+ only spend 90 mins exploring ggplot2 extension packages

+ create RNotebook tutorial for other classmates to learn from me

+ figure out how to use it, and develop an example on how to use it

+ 3: ggforce

    - making annotations

+ include documentation on: 

    - what I've been able to do

+ Step 2: Open RMarkdown

    - name and package on top of the file
    - load data and package will be utilizing
    - work through application of gg-extension package
    
+ Step 3: Show and document code to create a specialty visual

+ Step 4: Write a brief description of the primary purpose of the package and the function I am demonstrating

+ Step 5: Knit the RMarkdown and post the HTML file to the PA7 discussion page on Canvas


